Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-02-22 bbbq_article.tex
Add refs

The R package 'tmhmm' was developed to do the similar topology
predictions as our earlier study (that used 'TMHMM'), yet in an automated way.
'TMHMM' has a restrictive software license \richel{ref} and allows a user
to download a pre-compiled executable after confirmation he/she
is in academia. The R package respects this restriction
and allows the user to install and use TMHMM from within R,
as done in this study.
'tmhmm' has been submitted to and is accepted by CRAN.

@@

To be able to call, from R, the TMH prediction software 'PureseqTM' \richel{ref},
which is written in C, the package 'pureseqtmr' has been developed. 
'pureseqtmr' allows to install 'PureseqTM' and use most of its features.
Excluded are the features that are used by the 'PureseqTM' 
developers to verify the correctness of their work.
'pureseqtmr' has been submitted to and is accepted by CRAN.

@@

MHCnuggets is a free and open-source Python package to predict 
epitope affinity for many MHC-I and MHC-II variants \richel{ref}.
The R package 'mhcnuggetsr' allows one to install and use MHCnuggets
from within R.
Also 'mhcnuggetsr' has been submitted to and is accepted by CRAN.

>>>>

The R package 'tmhmm' was developed to do the similar topology
predictions as our earlier study (that used 'TMHMM'), yet in an automated way.
'TMHMM' has a restrictive software license (\cite{krogh2001predicting}) and allows a user
to download a pre-compiled executable after confirmation he/she
is in academia. The R package respects this restriction
and allows the user to install and use TMHMM from within R,
as done in this study.
'tmhmm' has been submitted to and is accepted by CRAN.

@@

To be able to call, from R, the TMH prediction 
software 'PureseqTM' (\cite{wang2019efficient}),
which is written in C, the package 'pureseqtmr' has been developed. 
'pureseqtmr' allows to install 'PureseqTM' and use most of its features.
Excluded are the features that are used by the 'PureseqTM' 
developers to verify the correctness of their work.
'pureseqtmr' has been submitted to and is accepted by CRAN.

@@

MHCnuggets is a free and open-source Python package to predict 
epitope affinity for many MHC-I and MHC-II variants (\cite{shao2020high}).
The R package 'mhcnuggetsr' allows one to install and use MHCnuggets
from within R.
Also 'mhcnuggetsr' has been submitted to and is accepted by CRAN.
